\Large \bf 3-Step, 1-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-06 paper.tex
Future work

\section{{\bfseries\sffamily TODO} Conclusion \& Future Work:}
\label{sec:org29a90c8}

\begin{itemize}
\item How will this system change with more users? How will this system change with more diverse data?
\begin{itemize}
\item EEG stability
\item Also breakdown/malfunction
\item Address with? Ambulatory settings, Exercise, alcohol, caffeine, etc.
\end{itemize}
\item How “hackable” is a passthought?
\begin{itemize}
\item Point from NSPW draft
\item Address with? Statistical analysis \& hacking existing classifiers
\end{itemize}
\item UX improvements/innovations?
\begin{itemize}
\item Dry electrodes?
\item Closed-loop system?
\end{itemize}
\end{itemize}

Closed-loop BCI system could help us understand how learning effects
on the human side might impact authentication performance, as the human and machine
co-adapt during multiple authentication attempts.
\end{document}

>>>>

\section{Future Work}

One primary question surrounds how our passthought system performance will change with a greater number of users, and with more diverse data. Our system specifically trains on negative examples of non-users; we do not yet know how this approach will scale. At the same time, we must investigate the stability of EEG readings for a passthought are over time. We must also collect EEG data from the variety of different user states: ambulatory settings, during physical exertion or exercise, under the influence of caffeine or alcohol, etc.

% We provide cursory evidence that passthoughts are difficult to spoof, though further work should expand on ours with more subjects.
Another important question surrounds how passthoughts might be cracked.
Generally, we do not understand how an individual's passthought is drawn from the general distribution of EEG signals that an individual produces throughout the day.
Given a large enough corpus of EEG data, are some passthoughts as easy to guess as \textit{password1234} is for passwords?
Future work should perform statistical analysis on passthoughts, such as clustering (perhaps with t-SNE) to better understand the space of possible passthoughts.
This work will allow us simulate cracking attempts, and to develop empirically motivated strategies for prevention, e.g. locking users out after a certain number of attempts.
This work could also reveal interesting tradeoffs between the usability and accuracy of certain passthoughts with their security properties.

Finally, our work leaves room for some clear UX improvements.
Future work should try using dry electrodes, commonly found in consumer EEG devices, for comfort and usability.
Future work should also attempt a closed-loop (or online) passthought system, in which users receive immediate feedback on the result of their authentication attempt. A closed-loop BCI system could help us understand how learning effects
on the human side might impact authentication performance, as the human and machine co-adapt during multiple authentication attempts.

\section{TODO Conclusion}

\end{document}
